Fictitious Play in Network Aggregative Games

### 2021-05-06 Documents/FP in NAGs/neurips_2020.tex
added stylefile

  In this section we aim to find some convergence structure for the case in which the NA game is
  not necessarily zero-sum. In particular, we  show that the NA-CTFP process converges to the set
  of coarse correlated equilibria \cite{}.

  \begin{definition}
    A distribution $\mathcal{D}$ over the joint action set $S = \times_\mu S^\mu$ is
    called a \emph{coarse correlated equilibrium} (CCE) if, for all $\mu$

    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{- \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

  In words, the above definition says that, if the agents are given a probability distribution
  with which the can play their actions, then the expected payoff, for all agents is greater than
  or equal to the payoff that they would get by playing any of their other available actions,
  assuming that the other agents keep to the distribution.

  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is drawn from a joint probability
  distribution $\mathcal{D}$, then there is a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu s^\nu$.
  Therefore, $\mathcal{D}$ is a probability distribution over all actions and all references.
  Consider, then, a vector of joint distributions over actions and references which is generated
  by CTFP. In particular, if by playing with CTFP, the agents reach the state $(\xmu)_{i = 1}^N$
  with references $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} = (\mathcal{D}^1, ...,
  \mathcal{D}^N)$ such that $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected payoff
  that the agent would receive for playing this strategy is

@@

    By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change. As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time. An agent achives \emph{no regret} if $R^\mu$ is non-positive.
  \end{remark}

@@

    For any agent $\mu$ define
    \begin{equation}
      \bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu)
    \end{equation}

@@

    We insert this into the previous equation to yield

>>>>

  In this section we aim to find some convergence structure for the
  case in which the NA game is not necessarily zero-sum. In
  particular, we show that the NA-CTFP process converges to the set of
  coarse correlated equilibria \cite{}.
  %
  \begin{definition}
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
    (CCE) if, for all $\mu$
    \begin{equation}
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})] \hspace{1cm} \forall j \in S^\mu.
    \end{equation}
  \end{definition}

  In words, the above definition says that, if the agents are given a
  probability distribution with which they can play their actions, then
  the expected payoff, for all agents is greater than or equal to the
  payoff that they would get by playing any of their other available
  actions, assuming that the other agents keep to the distribution.

  \fb{perhaps what is below could go into a theorem/lemma.}

  For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ \fb{$s$ is normally used for actions} is
  drawn from a joint probability distribution $\mathcal{D}$, then
  there is a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$.  Therefore, $\mathcal{D}$ is a probability
  distribution over all actions and all references.  Consider, then, a
  vector of joint distributions over actions and references which is
  generated by CTFP. In particular, if by playing with CTFP, the
  agents reach the state $(\xmu)_{i = 1}^N$ with references
  $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} =
  (\mathcal{D}^1, ..., \mathcal{D}^N)$ such that
  $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected
  payoff that the agent would receive for playing this strategy is

@@

    By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change. As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time. An agent achieves \emph{no regret} if $R^\mu$ is non-positive.
  \end{remark}

@@

    For any agent $\mu$ define \fb{what are we defining here?}
    \begin{equation}
      \bar{u}^\mu (\alpha_\sigma^\mu) := max_{y \in \Delta_\mu} u^\mu(y, \alpha_\sigma^\mu)
    \end{equation}

@@

    We insert this \fb{use enumeration} into the previous equation to yield
